---
start date: 4/21/2021
authors: Grant Armstrong, Aatika Rizwan, Damon Luk, Rishab Ayyappath, Jeremy Amand
title: "KickStarter DataMining"
output: html_notebook
---
Columns of interest include launched, state, main_category, category, deadline, backers, and country
 
Aatika - Import Data & Clean (remove all state='live' and 'canceled' rows) Make sure CSV is readable from the internet so we dont need
to keep it locally in our repository 
```{r}
raw<-read.csv("https://www.kaggle.com/kemical/kickstarter-projects?select=ks-projects-201801.csv")
```

supervised classification method 1 -predicting the value of the ‘state’ column (whether or not the project succeeds) based on values of other attributes.
Grant & Damon - Naive Bayes w/ 10 fold cross validation
```{r}
precisions<-c() #for storing performance measures for all 10 models
recalls<-c()
accuracies<-c()

#Randomly shuffle the data
yourData<-yourData[sample(nrow(yourData)),]

#Create 10 equally size folds
folds <- cut(seq(1,nrow(yourData)),breaks=10,labels=FALSE)

#Perform 10 fold cross validation
for(i in 1:10){
    #Segement your data by fold using the which() function 
    testIndexes <- which(folds==i,arr.ind=TRUE)
    testData <- yourData[testIndexes, ]
    trainData <- yourData[-testIndexes, ]
    
    
    #Use the test and train data partitions however you desire...
    classifier <- naiveBayes(trainData[,2:10], trainData[,11])
    tab<-table(predict(classifier, testData[,-11]), testData[,11])
    
    accuracies<-c(accuracies,(tab[1] + tab[4]) /(tab[1] + tab[3] + tab[4] +tab[2]))
    precisions<-c(precisions, tab[1][1]/(tab[1][1] + tab[3]) )
    recalls<-c(recalls,tab[1][1]/(tab[1][1] + tab[2][1]))
}

```

Performance of Naive Bayes
```{r}
print("Average Precision:")
sum(precisions) /10
print("Average Recall:" )
sum(recalls) /10
print("Average Accuracy:" )
sum(accuracies) /10
```


We are thinking of using a decision tree as another classification method 
to visualize the values of attributes that lead to success or failure
Jeremy & Rishab
```{r}

```

Performance of DT
```{r}


```


ROCR comparing Naive-Bayes to DT
```{r}

```


Aatika
Word Cloud of Successful Project Names
```{r}

```

